The Design and Implementation of the Synchronous Language \CEU

### 2016-09-30 paper.tex
(>) related work for stack-based internal events

\CEU has a strong influence from Esterel but differ in the most fundamental 
aspect of the notion of time.
%
In \CEU, instead of clock ticks, atomic external event occurrences that define 
time units.
%
The event-driven approach of \CEU is widespread~\cite{sync_async.whynotthreads} 
and popular in many software communities, such as web frameworks (e.g., 
\emph{jQuery}~\cite{js.jquery} and \emph{Node.js}~\cite{js.node}), GUI toolkits 
(e.g., \emph{Tcl/Tk}~\cite{tcl.tk} and \emph{Java Swing}~\cite{java.swing}), 
and Games~\cite{gamepatterns}.
%
We consider that this approach is more familiar to programmers and simplifies 
the reasoning about concurrency.
%
As far as we know, \CEU is the first to encrust this event-triggered notion of 
time in the core of the language, which is a prerequisite for the concurrency 
checks that enable safe shared-memory concurrency.
%
\CEU also the distinguishes external events from internal events.
Internal events support stack-based micro reactions within external reactions, 
providing more fine-grained control for intra-reaction execution.

>>>>

\CEU has a strong influence from Esterel but differ in the most fundamental 
aspect of the notion of time.
%
In \CEU, instead of clock ticks, atomic external event occurrences that define 
time units.
%
The event-driven approach of \CEU is widespread~\cite{sync_async.whynotthreads} 
and popular in many software communities, such as web frameworks (e.g., 
\emph{jQuery}~\cite{js.jquery} and \emph{Node.js}~\cite{js.node}), GUI toolkits 
(e.g., \emph{Tcl/Tk}~\cite{tcl.tk} and \emph{Java Swing}~\cite{java.swing}), 
and Games~\cite{gamepatterns}.
%
We consider that this approach is more familiar to programmers and simplifies 
the reasoning about concurrency.
%
As far as we know, \CEU is the first to encrust this event-triggered notion of 
time in the core of the language, which is a prerequisite for the concurrency 
checks that enable safe shared-memory concurrency.

In \CEU internal events support stack-based micro reactions within external
reactions, providing more fine-grained control for intra-reaction execution.
%
Some variants of Statecharts~\cite{statecharts} also distinguish internal from
external events~\cite{statecharts.variants}.
%Some variants of Statecharts support local events which imply handling intra
%reactions like Céu.
In Statemate, ``reactions to external and internal events (...) can be sensed only
after completion of the step''~\cite{statecharts.statemate}, implying queue-based
execution.
In Stateflow, ``the receiving state (of the event) acts here as a
function''~\cite{statecharts.stateflow}, which is similar to Céu's stack-based
execution.
To avoid recursion, Céu adopts delayed awaits, while in Statemate, ``loops in
the broadcasting of events (between states) are forbidden''.
